A Structural and Functional Bioinformatics Study of QTY-designed Retinylidene Proteins

### 2025-04-27 Paper/Source/manuscript.tex

In this paper, we apply the QTY code to redesign 9 human opsins and 3 microbial opsins. We provide superposition

@@

All MD simulations and analyses were executed on a desktop computer with Intel Xeon Platinum 8352V Processor, 256GB RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 24GB VRAM each. All MD simulations were conducted using GROMACS 2024.5 \citep{Abraham_2015} with the CHARMM36m all-atom force field \citep{Huang_2017}. The parameters for retinal were obtained from NAMD Wiki (\url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalTop} and \url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalPar}), and integrated manually into the files for the protein. Initial structures, configuration files and command-line codes for the simulations are publicly available at ... [ONLINE DATABASE TO BE PREPARED].

Regarding the native OPN2, the membrane-protein system was constructed using CHARMM-GUI’s web-based membrane builder and downloaded in GROMACS format \citep{Jo_2008, Wu_2014, Lee_2016}. The protein was centered in a rectangular box. The membrane models generated consisted 40\% POPC, 40\% POPE, 10\% POPS, and 10\% cholesterol, which simulate a rod photoreceptor disk membrane \citep{Albert_2005}. The system was solvated in TIP3P water with 150 mM NaCl. 11-cis-retinal was manually added to the protein files. Electrostatics were handled with Particle Mesh Ewald (PME), with both Coulomb and van der Waals interaction cutoffs set at 1.2 nm. System energy was minimized using the steepest descent until maximum forces converged below 1000 kJ/mol/nm. The standard six-step CHARMM-GUI NP$\gamma$T equilibration protocol \citep{Jo_2008} was used, with 2 125-ps NVT equilibration simulations, and 1 125-ps and 3 500-ps NP$\gamma$T equilibration simulations. Temperature and pressure were maintained at 303.15 K and 1.0 bar, respectively, using the V-rescale thermostat and C-rescale barostat with surface-tension coupling. The LINCS algorithm was used for constraints. Verlet integrator was used. Following equilibration, a 10-ns production MD simulation was run. Then, the retinal molecule was manually switched to all-trans state by rotating C13 to C15 and bonded hydrogens and methyl groups by 180 degrees around the C11-C12 bond. Energy minimization and equilibration were repeated exactly as before, and then a 200-ns production MD simulation was run.

Regarding the QTY-designed OPN2, the system was constructed directly using GROMACS. The protein was centered in a rectangular box of identical size with that of native OPN2. The system was solvated in TIP3P water with 150mM NaCl. 11-cis-retinal was manually added to the protein files. System energy was minimized using the steepest descent until maximum forces converged below 1000 kJ/mol/nm. Electrostatics were handled with Particle Mesh Ewald (PME), with both Coulomb and van der Waals interaction cutoffs set at 1.2 nm. The equilibration process is designed to align with that of the native protein, with 1 250-ps NVT equilibration simulation, and 1 125-ps and 1 1500-ps NPT equilibration simulations. Temperature and pressure were maintained at 303.15 K and 1.0 bar, respectively, using the V-rescale thermostat and C-rescale barostat with isotropic coupling. The LINCS algorithm was used for constraints. Verlet integrator was used. Following equilibration, a 10-ns production MD simulation was run. Then, the retinal molecule was manually switched to all-trans state by rotating C13 to C15 and bonded hydrogens and methyl groups by 180 degrees around the C11-C12 bond. Energy minimization and equilibration were repeated exactly as before, and then a 200-ns production MD simulation was run.

>>>>

In this paper, we apply the QTY code to redesign 9 human opsins and 3 microbial opsins. We provide the superpositions of the AlphaFold3-predicted hydrophobic native proteins and their water-soluble QTY variants, and experimentally-determined structures when available. We also provide the comparative surface hydrophobicity of the variants. Furthermore, we run MD simulations of native and QTY-designed OPN2 and analyze their response to the 11-cis to all-trans isomerization of the retinal chromophore.

@@

All MD simulations and analyses were executed on a desktop computer with Intel Xeon Platinum 8352V Processor, 256GB RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 24GB VRAM each. All MD simulations were conducted using GROMACS 2024.5 \citep{Abraham_2015} with the CHARMM36m all-atom force field \citep{Huang_2017}. Data for retinal were obtained from NAMD Wiki (\url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalTop} for topology and \url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalPar} for parameters) and manually integrated into the protein file. Initial structures, configuration files, and command-line codes for the simulations are publicly available at... [ONLINE DATABASE TO BE PREPARED].

Regarding native OPN2, the membrane protein system was constructed using the web-based membrane builder CHARMM-GUI and was downloaded in GROMACS format \citep{Jo_2008, Wu_2014, Lee_2016}. The protein was centered in a rectangular box. The generated membrane models consisted of 40\% POPC, 40\% POPE, 10\% POPS, and 10\% cholesterol, which simulate a rod photoreceptor disk membrane \citep{Albert_2005}. The system was solvated in TIP3P water with 150 mM NaCl. 11-cis-retinal was manually added to the protein files. LINCS constraints was used for constraints and Verlet integrator was used. Electrostatics was handled with Particle Mesh Ewald (PME), with both Coulomb and van der Waals interaction cutoffs set at 1.2 nm. The energy of the system was minimized using the steepest descent until the maximum forces converged below 1000 kJ/mol/nm. The standard six-step CHARMM-GUI NP$\gamma$T equilibration protocol \citep{Jo_2008} was used, with two 125-ps NVT equilibration simulations, and one 125-ps and three 500-ps NP$\gamma$T equilibration simulations. Temperature and pressure were maintained at 303.15 K and 1.0 bar, respectively, using the V-rescale thermostat and C-rescale barostat with surface-tension coupling. Following equilibration, a 10-ns production MD simulation was run. The retinal molecule was then manually switched to the all-trans state by rotating C13 to C15 and bonded hydrogen and methyl groups by 180 degrees around the C11-C12 bond. Energy minimization and equilibration were repeated exactly as before, and then a 200-ns production MD simulation was run.

Regarding QTY-designed OPN2, the system was constructed directly using GROMACS. The protein was centered in a rectangular box with dimensions equivalent to those of the native OPN2. The equilibration involved a sequence of simulations: a 250-ps NVT equilibration, followed by 125-ps and 1500-ps NPT equilibrations, totaling an equilibration duration that matches that of the natural OPN2. All other configurations and parameters are identical to those of the original OPN2.
